What is essential?

### 2016-03-14 paper/presentation/presentation.tex
add some color

\section{Objective}
\subsection{Research Question}
\begin{Slide}{Research question}
In the context of software requirements engineering education:
\begin{itemize}
\item How to choose a set of \\ \Emph{essential requirements engineering concepts} \\ that allows for sufficient expressiveness, \\ without overloading the metamodel with esoteric concepts just for the sake of completeness?
\end{itemize}
\end{Slide}
\subsection{Approach}
\begin{Slide}{Approach}
Make a survey among RE scholars:
\begin{itemize}
\item How to quantify ''essentiality''?
\pause
\item One possible quantification: \\ The more scholars that agree on a definition of a concept \\ and \\ the more scholars that use the concept, \\ the more essential is the concept.
\end{itemize}
\end{Slide}

>>>>

\section{Objective}
\subsection{Research Question}
\begin{Slide}{Research question}
In the context of software requirements engineering education:
\begin{itemize}
\item How to choose a set of \\ \Emph{essential requirements engineering concepts} \\ that allows for \Alert{sufficient expressiveness}, \\ without overloading the metamodel with esoteric concepts just for the sake of \Alert{completeness}?
\end{itemize}
\end{Slide}
\subsection{Approach}
\begin{Slide}{Approach}
Make a survey among RE scholars:
\begin{itemize}
\item How to quantify ''essentiality''?
\pause
\item One possible quantification: \\ The more scholars that \Emph{agree} on a definition of a concept \\ and \\ the more scholars that \Emph{use} the concept, \\ the more essential is the concept.
\end{itemize}
\end{Slide}
